Analysis of pudding following Davidson 1970

### 2021-11-02 inst/pudding.Rmd
scatterplot

```{r}
print(hankin)
print(davidson)
par(pty="s")
plot(c(t(hankin)),c(t(davidson)),col=c('red','green','blue'),pch=16,asp=1,xlim=c(0.25,0.45),ylim=c(0.25,0.45),type='b')

>>>>

```{r}
print(hankin)
print(davidson)
par(pty="s")
plot(c(t(hankin)),c(t(davidson)),col=c('red','green','blue'),pch=16,asp=1,xlim=c(0.25,0.45),ylim=c(0.25,0.45))
for(i in seq_len(nrow(hankin))){
text(hankin[i,1],davidson[i,1],rownames(hankin)[i],pos=4)
text(hankin[i,2],davidson[i,2],rownames(hankin)[i],pos=4)
text(hankin[i,3],davidson[i,3],rownames(hankin)[i],pos=4)

segments(x0=hankin[i,1],y0=davidson[i,1], x1=hankin[i,2],y1=davidson[i,2])
}
